### 2023-11-25 main.tex
''
partial

		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt

@@

	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1}^{N-1}(n_{b}^{x}-n_{a}^{x})

@@

	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq d}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt

@@

	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}. We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$. Thus, we have

@@

	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\right)\nonumber\\=&

@@

where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain

@@

		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\right)\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that

@@

	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 

@@

Indeed
	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
while for every $c\in \{1,\ldots,N-2\}$ we have 
		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
		\sum_{k=1}^{N-1}n_{k}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
		\nu(n_{q}^{x+1}-n_{d}^{x})
where we call $q$ such that $h_{c}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$. Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
Moreover
	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.

@@

		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}

>>>>

		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}\dt

@@

	\mathcal{L}^{rd}n_{a}^{x}=\nu\sigma_{11}\Delta_{L}n_{a}^{x}+\nu\sigma_{12}\sum_{b=1\,:\,b\neq a}^{N-1}\Delta_{L}n_{b}^{x}+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}(n_{b}^{x}-n_{a}^{x})

@@

	\mathcal{L}^{rd}n_{a}^{1}=\sigma_{11}\nu \left(\rho_{a}^{0}-2n_{a}^{1}+n_{a}^{2}\right)+\sigma_{12}\nu\sum_{b=1\,:\,b\neq a}^{N-1}\left(\rho_{b}^{0}-2n_{b}^{1}+n_{b}^{2}\right)+\Upsilon\sum_{b=1\,:\,b\neq a}^{N-1}\left(n_{b}^{1}-n_{a}^{1}\right)\dt

@@

	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
Duality for the right boundary is similar. \\

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}
We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}. We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}^{1}+r_{\ell}^{1}}$. Thus, we have

@@

	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\nonumber\\=&

@@

Where we used {\color{blue}
\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\frac{\nu!}{r_{1}!\cdots r_{N}!}=\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}
&\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}-\xi_{a}^{1}+\xi_{a}^{1}}\right)\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{\ell}+r_{\ell}}\right)\\=&	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}
and }the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain

@@

		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
where we used the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that

@@

	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
%The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 

@@

Indeed we have that 
	\item \textit{Stirring generator}:

\begin{equation}
	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)
\end{equation}
The only terms that survive are: in one case the ones with $a=d$ and $b\neq d$, giving a contribution $-n_{d}^{x}n_{b}^{x+1}$; in the other case the ones with $a\neq d$ and $b=d$, giving a contribution $n_{a}^{x}n_{d}^{x+1}$. Thus we obtain 
\begin{align*}
	\mathcal{L}_{x,x+1}n_{d}^{x}=&\sum_{a=1\,:\,a\neq d}^{N}n_{a}^{x}n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N}n_{d}^{x}n_{b}^{x+1}\\
	=&\sum_{a=1\,:\,a\neq d}^{N-1}n_{a}^{x}n_{d}^{x+1}+(\nu-\sum_{i=1}^{N-1}n_{i}^{x})n_{d}^{x+1}-\sum_{b=1\,:\,b\neq d}^{N-1}n_{d}^{x}n_{b}^{x+1}-n_{d}^{x}(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1})\\
	=&\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)
\end{align*} 
where we have used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$.
\item \textit{Stirring-mutation generator}: for every $c\in \{1,\ldots,N-2\}$ we have 
\begin{equation}
	\begin{split}
		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{h_{c}(b)}^{x}+\bm{\delta}_{h_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{k=1}^{N}n_{k}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
		\\&=
		\sum_{k=1}^{N-1}n_{k}^{x}n_{q}^{x+1}+\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=1}^{N-1}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=1}^{N-1}n_{i}^{x+1}\right)
		\\&=
		\nu(n_{q}^{x+1}-n_{d}^{x})
	\end{split}
\end{equation}
where we call $q$ such that $h_{c}^{-1}(d)=q$ and we used the fact that $n_{N}^{x}=\nu-\sum_{i=1}^{N-1}n_{i}^{x}$. Let us observe that, by the definition of the map $h_{c}(\cdot)$ and for the fact that $1\leq c\leq N-2$, we have that $q\neq d$ and $q\neq N$ .
Moreover
\begin{equation}
	\mathcal{L}_{x,y}^{m}n_{d}^{x}=\sum_{a,b=1}^{N-1}n_{a}^{x}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-n_{d}^{x}\right)=\sum_{b=1}^{N-1}(n_{b}^{x}-n_{d}^{x})
\end{equation}
\end{enumerate}
Then, summing over all indices $c\in\{1,\ldots,N-2\}$, we obtain \eqref{actionGraphRD}.

@@

		\mathcal{L}_{\text{left}}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{1}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
